\documentclass[14pt]{beamer}
\usetheme{Pittsburgh}
\usepackage[utf8]{inputenc}
\usepackage[portuguese]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Alexandre Neto}
\title{\textit{IoT} Aplicado à Segurança Pública}
\institute{
	Análise e Desenvolvimento de Sistemas\\
	Fatec-SJC
	}
%\setbeamercovered{transparent} 
%\setbeamertemplate{navigation symbols}{} 
%\logo{} 
%\institute{} 
%\date{} 
%\subject{} 
\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}
\frametitle{Agenda}
\tableofcontents
\end{frame}

\section{Tema}
\begin{frame}
\frametitle{Tema}
This is a text in first frame. This is a text in first frame. This is a text in first frame.
\begin{itemize}
 \item<1-> Text visible on slide 1
 \item<2-> Text visible on slide 2
 \item<3> Text visible on slide 3
 \item<4-> Text visible on slide 4
\end{itemize}
\end{frame}

\begin{frame}
 In this slide \pause
 
 the text will be partially visible \pause
 
 And finally everything will be there
\end{frame}



\begin{frame}
\frametitle{Sample frame title}
 
In this slide, some important text will be
\alert{highlighted} beause it's important.
Please, don't abuse it.
 
\begin{block}{Remark}
Sample text
\end{block}
 
\begin{alertblock}{Important theorem}
Sample text in red box
\end{alertblock}
 
\begin{examples}
Sample text in green box. "Examples" is fixed as block title.
\end{examples}
\end{frame}



\begin{frame}
\frametitle{Two-column slide}
 
\begin{columns}
 
\column{0.5\textwidth}
This is a text in first column.
$$E=mc^2$$
\begin{itemize}
\item First item
\item Second item
\end{itemize}
 
\column{0.5\textwidth}
This text will be in the second column
and on a second tought this is a nice looking
layout in some cases.
\end{columns}
\end{frame}



\end{document}